---
title: plot_it function
author: |  
 | Matthew Malishev^1^*
 |  
 | _^1^ Department of Biology, Emory University, 1510 Clifton Road NE, Atlanta, GA, USA, 30322_
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
fontsize: 10
geometry: margin=1in
documentclass: article
linkcolor: pink
urlcolor: blue
citecolor: red
always_allow_html: yes
output:
  md_document: 
    variant: markdown_github
  pdf_document:
    includes:
      in_header: # add .tex file with header content
    highlight: tango
    template: null
    toc: yes
    toc_depth: 4
    number_sections: false
    fig_width: 4
    fig_height: 5
    fig_caption: true
    df_print: tibble 
    citation_package: biblatex # natbib
    latex_engine: xelatex #pdflatex # lualatex
    keep_tex: true # keep .tex file in dir 
  html_document:
    highlight: tango
    code_folding: hide
    toc: yes
    toc_depth: 4
    number_sections: no
    toc_float: yes
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
    toc_depth: 4
inludes:
  before_body: before_body.tex
subtitle: 
tags:
- nothing
- nothingness
params: 
  dir: "/Users/malishev/Documents/Melbourne Uni/Programs/R code/plot_it"
  date: !r Sys.Date()
  version: !r getRversion()
  email: "matthew.malishev@gmail.com"
  doi: https://github.com/darwinanddavis/plot_it
classoption: portrait
vignette: >
  %\VignetteIndexEntry{plot_it}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---
<!-- This file is edited in README.Rmd -->

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = F, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir
```

# `plot_it` function    

`R` version: `r params$version`    

\newpage      

## Overview
Plotting function for switching between manuscript-ready and presentation style plots in `R`.    

### Directions
:one: In your `R` file, run the following code.  

```{r}
require(RCurl)
script <- getURL("https://raw.githubusercontent.com/darwinanddavis/plot_it/master/plot_it.R", ssl.verifypeer = FALSE)
eval(parse(text = script))
```  

:two: Use the following function to set your plotting parameters.  

- Specify if plotting for a manuscript or seminar (0/1)  
- Specify background colour (char)  
- Specify plotting colour palette 1 from RColorBrewer (char)  
- Specify plotting colour palette 2 from RColorBrewer (char)  
- Specify alpha transparency for plot points (int)  
- Specify font family for plot text (char)  

```{r}
require(RColorBrewer)
display.brewer.all()
# Set global plotting parameters
cat("plot_it( \n0 for presentation, 1 for manuscript, \nset colour for background, \nset colour palette 1. use 'display.brewer.all()', \nset colour palette 2. use 'display.brewer.all()', \nset alpha for colour transperancy, \nset font style \n)")

plot_it(0,"blue","Spectral","Greens",1,"mono") # set plot function params       
plot_it_gg("black","white") # specify background and foreground colours   
```  

:three: Make cool graphs.  

## Maintainer  

**Matt Malishev**
\      
[Website](https://www.researchgate.net/profile/Matt_Malishev)  
\    
[@darwinanddavis](https://twitter.com/darwinanddavis)  
\    
matthew.malishev [at] gmail.com  
\    